Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-26 paper/paper.tex
added spark implementation details of sector change detection workload

The goal of sector change detection workload is to detect the  enter or leaving of aircraft from one air sector to other, by processing the trajectories stream. Given that the dataset of sectors (i.e., polygons) available as reference to check against it, also it used to assign the corresponding sector for certain aircraft's position. In this workload, providing the  global model of data (sectors dataset) in streaming processing workload is tested.Moreover, preserving the stream records order and parallel streams consuming are covered.

 The implementation details of this workload in Spark and Flink are presented in the following: 
 \begin{itemize}
 \item {\bf{Implementation in Spark }}

 we implement this workload, based on the following operation stages: 
 \begin{enumerate*}[label={\alph*)}]
 \item receive and build the trajectories stream 
 \item manage the aggregate state and assign the sector for each trajectory.
 \item identify the  change of sector per trajectory if exist
 \end{enumerate*}

 figure 4 shows the Spark streaming APIs used to implement trajectory's sector change detection workload. First, the trajectories stream is built using \texttt{mapToPair}, \texttt{filter}, and \texttt{groupByKey} APIs as was discussed in statistics computation workload. Second,  \texttt{updateStateByKey} API is used to assign corresponding sector for all new aircraft positions in  micro batch  and aggregate last position in previous batch. Finally, the detection of sector change is done by extra filtering transformation using \texttt{filter} API, by identifying the change of sectors in each trajectory. While the sector data set is provided using the \texttt{Broadcast} feature in Spark.
 \begin{figure}[h]

   \centering

      \caption{Spark streaming implementation of sector change detection workload.}
 \end{figure}

>>>>

The goal of sector change detection workload is to detect the  enter or leaving of aircraft from one air sector to other, by processing the real-time stream of trajectories. Given that the dataset of sectors (i.e., polygons) is available as reference to assign the corresponding sector for certain aircraft's position. In this workload, we test the aspect of providing the  global model of data (sectors dataset) in streaming processing workload. Moreover, the preserving od stream's records order and consuming of parallel Kafka streams points were covered.

 The implementation details of this workload in Spark and Flink are presented in the following:

 \begin{itemize}
 \item {\bf{Implementation in Spark }}

 We implemented the sector change detection workload in Spark by constructing the trajectories stream and assigning the sectors for each position in all trajectories, then a change between the assigned sectors of two consecutive aircraft's positions is marked as alert case. First, a multiple instances of \texttt{DStream} are created using \texttt{KafkaUtils.createDirectStream} to read in  parallel from Kafka, after  all input data streams are combined using \texttt{union} function. Second, the records (i.e., ADS-B messages) of the resulted union stream are parsed and mapped to tuples of (aircraft ID, position message) using defined \texttt{mapToPair} transformation. Third, the unrelated  tuples are filtered based on the message type through \texttt{filter} operation. Fourth, the trajectories stream is constructed by combining all tuples with the same ID using the \texttt{groupByKey} function. Then, to manage and aggregate the state of trajectories stream between the mini-batches a configured \texttt{updateStateByKey} function is applied,  the corresponding sector are assigned, the old positions of certain trajectory from previous batch are discarded, but the last position of old batch is kept to be used alongside with the new positions.
 The sector data set is provided using the \texttt{Broadcast} shared value feature in Spark that distributes the  data set to all cluster nodes efficiently. Finally, the detection of sector change is done by extra filtering transformation using \texttt{filter}, by checking the sector of the positions list in each tuple.
